Plant-pollintor networks worldwide are composed by the same specific building

### 2021-07-28 Draft/Draft.Rmd

  yup = rep(1,length(labup))

@@

  ggplot() +
    scale_shape_identity() +
    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), 
                 size = 1, color = "grey20")+  geom_scatterpie(aes(x=x, y=y, group=position,r=.4), 
    data = d_nodes_pollinator, cols=as.character(c("Bee","Birds","Coleoptera","Lepidoptera",
     "Lizards","Non-bee-Hymenoptera", "Non-syrphids-diptera","Other_insects",
     "Syrphids"))) +
    geom_scatterpie(aes(x=x, y=y, group=position,r=0.4), 
                    data = d_nodes_plant,
                    cols=as.character(c("1","2","3","4","5")))+
    coord_fixed()+
    scale_fill_manual(values = mycolors,"test",
      breaks=c("Bee","Birds","Coleoptera","Lepidoptera",
               "Lizards","Non-bee-Hymenoptera", "Non-syrphids-diptera","Other_insects",
               "Syrphids","1","2","3","4","5"), labels=c("Bee","Birds","Coleoptera","Lepidoptera",
                                                        "Lizards","Non-bee-Hymenoptera", "Non-syrphids-diptera","Other_insects",
                                                        "Syrphids", 
          "Selfing herbs","Small outcrossing perennials","Self-incomp. perennials\nwith large flowers",
          "Tall plants with small\nunisexual flowers","Short-lived outcrossers with\nlong zygomorphic flowers"))+
    xlim(-1.5,4)+ ylim(-0.5,1.5)+
    theme(panel.background = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank())+
    labs(x=NULL,y=NULL)+
    guides(color = FALSE,fill=guide_legend(title="Functional groups"))+
    ggtitle(paste0("Motif ",motif_number))+
    theme(plot.title = element_text(hjust = 0.5),legend.key.size = unit(0.5, 'cm'))+
    theme(plot.margin=unit(c(0,0,0,0),"cm"))
}

>>>>

  yup = rep(2,length(labup))

@@

  ggplot() +
    scale_shape_identity() +
    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), 
                 size = 1, color = "grey20")+  geom_scatterpie(aes(x=x, y=y, group=position,r=.45), 
    data = d_nodes_pollinator, cols=as.character(c("Bee","Birds","Coleoptera","Lepidoptera",
     "Lizards","Non-bee-Hymenoptera", "Non-syrphids-diptera","Other_insects",
     "Syrphids"))) +
    geom_scatterpie(aes(x=x, y=y, group=position,r=0.45), 
                    data = d_nodes_plant,
                    cols=as.character(c("1","2","3","4","5")))+
    coord_fixed()+
    scale_fill_manual(values = mycolors,"test",
      breaks=c("Bee","Birds","Coleoptera","Lepidoptera",
               "Lizards","Non-bee-Hymenoptera", "Non-syrphids-diptera","Other_insects",
               "Syrphids","1","2","3","4","5"), labels=c("Bee","Birds","Coleoptera","Lepidoptera",
                                                        "Lizards","Non-bee-Hymenoptera", "Non-syrphids-diptera","Other_insects",
                                                        "Syrphids", 
          "Selfing herbs","Small outcrossing perennials","Self-incomp. perennials\nwith large flowers",
          "Tall plants with small\nunisexual flowers","Short-lived outcrossers with\nlong zygomorphic flowers"))+
    xlim(-1.5,4)+ ylim(-0.5,2.5)+
    theme(panel.background = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank())+
    labs(x=NULL,y=NULL)+
    guides(color = FALSE,fill=guide_legend(title="Functional groups"))+
    ggtitle(paste0("Motif ",motif_number))+
    theme(plot.title = element_text(hjust = 0.5),legend.key.size = unit(0.5, 'cm'))+
    theme(plot.margin=unit(c(0,0,0,0),"cm"))
}
